### 2016-09-26 results.tex
modified DS privacy proof so that it follows from Jon's meta result

\todo{Privacy theorem for the ``plain'' linear-PRF scheme. Does not
  follow from Jon's general theorem.}

@@

\begin{theorem}\label{thm:ds-ss}
Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.  For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ such that, for any adversary~$A$
\[
\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}[Proof (sketch). ] \todo{Move this sketch to be a proof
    of Jon's meta-result. Downgrade theorem to be a corollary of that
    result, the proof simply being a description of how $\Rep$
    decomposes into $\Rep_1$ and $\Rep_2$.}
Adversary~$B^{f}$ simulates the steps of $\ExpPrivSSreal{\Pi_{\mathrm{ds}}}{A}$, using its oracle to simuate~$\Rep(S)$.  When~$f=F_K$ then the simulation is perfect.  When~$f=\rho$ then~$B$ simulates $\ExpPrivSSreal{\overline{\Pi}_{\mathrm{ds}}}{A}$ where $\overline{\Rep}$ effectively uses~$k$ independent random functions as the hash functions.  But the $\pub$ produced by $\overline{\Rep}$ has a distribution that depends only~$|S|=n$, not the specific elements of~$S$, and the other public parameters~$m,k$.  Thus, a simulator~$\Sim$ given only $\leak(S)=|S|$ can produce a correct~$\pub$ as follows: starting with an all-zeros array~$M$ of length~$m$, uniformly sample (with replacement)~$nk$ integers in~$[m]$ and set the resulting positions of~$M$ to 1.
\end{proof}

>>>>

\todo{Privacy theorem for the ``plain'' linear-PRF scheme.  Follows from Jon's general theorem.}

@@

The privacy of $\Pi_{\mathrm{ds}}$ follows directly from our general
result, Theorem~\ref{thm:xxx}.

\begin{theorem}\label{thm:ds-ss}
Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.  For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ such that, for any adversary~$A$
\[
\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
The decompose $\Rep$ into $\Rep_1$ and $\Rep_2$ as follows.  On input
$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.  On input $n,F_K(s_1),\ldots,F_K(s_{kn})$, algorithm $\Rep_2$ simply initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)]$ to 1.  It returns~$M$ as $\pubaux$.
\end{proof}

\fixme{The following is left only for cut-and-paste value.}
\begin{theorem}\label{thm:ds-ss}
Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.  For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ such that, for any adversary~$A$
\[
\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}[Proof (sketch). ] \todo{Move this sketch to be a proof
    of Jon's meta-result. Downgrade theorem to be a corollary of that
    result, the proof simply being a description of how $\Rep$
    decomposes into $\Rep_1$ and $\Rep_2$.}
Adversary~$B^{f}$ simulates the steps of $\ExpPrivSSreal{\Pi_{\mathrm{ds}}}{A}$, using its oracle to simuate~$\Rep(S)$.  When~$f=F_K$ then the simulation is perfect.  When~$f=\rho$ then~$B$ simulates $\ExpPrivSSreal{\overline{\Pi}_{\mathrm{ds}}}{A}$ where $\overline{\Rep}$ effectively uses~$k$ independent random functions as the hash functions.  But the $\pub$ produced by $\overline{\Rep}$ has a distribution that depends only~$|S|=n$, not the specific elements of~$S$, and the other public parameters~$m,k$.  Thus, a simulator~$\Sim$ given only $\leak(S)=|S|$ can produce a correct~$\pub$ as follows: starting with an all-zeros array~$M$ of length~$m$, uniformly sample (with replacement)~$nk$ integers in~$[m]$ and set the resulting positions of~$M$ to 1.
\end{proof}
\fixme{The above is left only for cut-and-paste value.}
